% Curriculum Vitae

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
\item\small{
\textbf{#1}{ #2 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Yadhukrishnan.P}} \\
Chennai, India $\cdot$\href{linkedin.com/in/yk2310/}{linkedin.com/in/yk2310/}\\
+91 9962585789 $\cdot$ \href{github.com/yk-2310}{github.com/yk-2310}\\
\href{mailto:yadhukrishnannair99@gmail.com}{yadhukrishnannair99@gmail.com}
$\cdot$
\href{mailto:yadhukrishnan17191@cse.ssn.edu.in}{yadhukrishnan17191@cse.ssn.edu.in}\\

\end{tabular*}

\section{About}
I am an Undergraduate Student pursuing Computer Science and Engineering interested in Web Development, Machine Learning, Data Science and Programming. 

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Sri Sivasubramaniya Nadar College of Engineering}{Chennai}
{B.E. Computer Science and Engineering; Affiliated to Anna University; GPA: 8.2 (4 semesters)}{2017 -- 2021}
\resumeItemListStart
\resumeItem{Activities \& Societies:}{Competitive Programming Club, Google Developer Student Club}
\resumeItemListEnd
\resumeSubheading
{DAV Public School}{Chennai}
{High School: Computer Science; CBSE; Class X 10 CGPA; Class XII 93.6\% (468/500)}{2003 -- 2017}
\resumeItemListStart
\resumeItem{Activities \& Societies:}{Math Club, English Club, Creative Writing, Science Quiz}
\resumeItem{Sports:}{Volleyball, Football, Badminton}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{National Centre for Coastal Research}{Chennai}
{Student Intern}{Apr.2019 - May.2019}
\resumeItemListStart
\resumeItem{Web Development Intern:}
{Worked on a project that required me to develop a dashboard user-interface for an application that the organization was developing.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeItem{Machine Learning:}{Octave,Python}
\resumeItem{Languages:}{Python, C, C++, Shell, Java, HTML, CSS, SQL}
\resumeItem{Frameworks:}{Pandas, Git (Version Control)}
\resumeItem{Other software skills:}{LaTeX, Microsoft Office, Google Cloud Platform}
\resumeItem{Soft Skills:}{Leadership, Communication, Problem Solving, Flexible \& Adaptible} 
\resumeSubHeadingListEnd



\section{Projects and Research}
\resumeSubHeadingListStart
\resumeItem{Pneumonia Prediction using Chest X-Ray (Sep.2019):}{An Application that allows the patients to upload their chest X-Ray in order to predict Pneumonia. The prediction is done using Image Classification using Machine Learning. The project was implemented as a web application and integrated using flask. }
\resumeItem{Pyschiatrist Assistance System (Aug. 2019 - Present):}{An Internally Funded Project to analyse a psychiatric patient and predict the depression level and the treatment required. The project is designed to be implemented using Image processing and Audio analysis.}
\resumeItem{SSN Web Application (Jun. 2019 - Oct. 2019):}{}
\resumeSubHeadingListEnd


\section{Courses and Certifications}
\resumeSubHeadingListStart
\resumeItem{Machine Learning:}{Stanford University, Coursera}
\resumeItem{Python for Data Science:}{University of Michigan, Coursera}
\resumeItem{GCP Fundamentals:}{Google, Coursera}
\resumeItem{Convolutional Neural Networks:}{Workshop at SSN College of Engineering}
\resumeItem{University Courses:}{Python Programming, C Programming, Mathematics - I and II, Discrete Mathematics, Probability and Queuing Theory, Data Structures, Object Oriented Programming, Design and Analysis of Algorithms, Digital Principles and System Design, Computer Architecture, Operating Systems, Database Management Systems, Computer Networks, Theory of Computation}
\resumeSubHeadingListEnd


\section{Achievements}
\resumeSubHeadingListStart
\resumeItem{}{Runner up, exLog-2018 (a state level Maths Quiz at SSN College of Engineering)}
\resumeItem{}{Finalist, Competitive Coding, The Mathrix, CEG Chennai}
\resumeItem{}{Runner Up in National Mathematics Day Quiz, SSN College of Engineering}
\resumeSubHeadingListEnd


\section{Languages}
English $\cdot$ Tamil $\cdot$ Hindi $\cdot$ Malayalam  $\cdot$ German

\section{Hobbies}
 $\cdot$ Music $\cdot$ Anime $\cdot$ Sports $\cdot$ Books $\cdot$ TV Shows

\lfoot{\small Last Updated: 17 Oct 2019}

\end{document}
